---
title: "Practical Machine learning final course"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goal of the project

The goal of the project is to predict the manner in which some volunteers did 
sports exercises. 
The variable to predict is the "classe" variable in the training set.

## We import the data and look inside

```{r import data and vizualisation}
data1<-read.table("pml-training.csv",na.strings=c("","NA"),sep=",",header=T)
str(data1)
```
## We clean it

There's a lot of variables which contain too much missing values.
We can see from this graph that many variables have a lot of missing values.

```{r data vizualisation, message=FALSE, warning=FALSE}
if(!require("Amelia")){
  install.packages("Amelia")
}
library(Amelia)
missmap(data1, main = "Missing values vs observed")
```

I remove the variables when they contain more than 50% missing values for analysis. 
I do not consider it appropriate and that it is useless to rectify them.

```{r cleaning data-1, message=FALSE, warning=FALSE}
# Count the number of missing values in each of the columns
nbna<-sapply(data1,function(x) sum(is.na(x)))
#I delete the variable if more than half of the observations are missing
ina<-which(nbna >8311)
ina<-as.data.frame(ina)

for (i in ina)
   {
    data1[,i]<-NULL
  }
```

I also delete the first 7 variables that are not suitable for analysis.

```{r cleaning data-2, message=FALSE, warning=FALSE}
data2<-data1[,-c(1:7)]
```


## Since there are many variables, I choose a random forest as a model, using the CARET package

```{r model, message=FALSE, warning=FALSE}

# creation of a training set and a test set

library(caret)

inTrain <- createDataPartition(y=data2$classe,
                               p=0.7, list=FALSE)
training <- data2[inTrain,]
testing <- data2[-inTrain,]

# launching of the model

modFit <- train(classe~ .,data=training,method="rf",prox=TRUE)
modFit

print(modFit)

## Predicting new values

pred <- predict(modFit,testing)

#confusion matrix

table(pred,testing$classe)
```



